\documentclass[11pt]{article}
\usepackage[margin=1.05in]{geometry}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{array}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{tcolorbox}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}
\definecolor{navy}{HTML}{16294A}
\definecolor{sred}{HTML}{D7263D}
\usepackage{sectsty}
\allsectionsfont{\color{navy}}
\newtcolorbox{keybox}{colback=blue!4!white,colframe=navy,boxrule=0.6pt,arc=2mm}
\newcommand{\henv}{\ensuremath{h_{\mathrm{env}}}}
\newcommand{\dodo}[1]{\ensuremath{\operatorname{do}(#1)}}
\setlength{\parskip}{3pt}

\title{\color{navy}\textbf{The Environment Tower: An Identity-Free Neural
Encoder of Hockey Context}\\[4pt]
\large OptBot Phase A --- design rationale, specification, and honest limits}
\author{OptBot Research \\ \small companion to \texttt{ARCHITECTURE\_PLAN.md} v2.2 \; \textperiodcentered\; regenerable from \texttt{scripts/21--25}}
\date{July 2026}

\begin{document}
\maketitle

\begin{abstract}
\noindent A hockey player's observed statistics blend who he is with what
surrounded him: linemates, opponents, coach, score state, zone, fatigue, rink.
Any system that projects a player onto a \emph{new} team must separate the two,
because the question itself is ``keep the player, swap the surroundings.''
Phase~A is a small ($\sim$2M parameter) neural encoder with one job: compress
everything surrounding a player during a stretch of ice time into a single
vector \henv{} while \textbf{provably knowing nothing about the player himself}.
We motivate the identity-free constraint against two rejected alternatives,
specify every input and every exclusion with its measured evidence, describe the
training-time failure modes and the probe gates that catch them, derive the
double-counting obligation (K-1) that the tower imposes on the player-side
model, and state candidly where the tower serves --- and where it is
\emph{not required by} --- the October 2026 proof event.
\end{abstract}

\section{The problem, stated precisely}
For player $p$, destination environment $E'$, and decision time $t_0$, we seek
\begin{equation}
\theta(p, E', t_0) \;=\; \mathbb{E}\!\left[\, Y_{1:40} \;\middle|\;
\dodo{E \sim E'},\; \mathcal{H}_p(<\!t_0) \,\right],
\label{eq:estimand}
\end{equation}
the expected on-ice impact over the first $\sim$40 games if the environment is
\emph{set} to $E'$, conditioned only on information knowable before $t_0$.
The operator $\dodo{\cdot}$ is the entire company. Associational models learn
that players in good environments produce more; a trade decision needs the
effect of \emph{placing} this player into that environment. A model can be
excellent at prediction and useless for the intervention.

For \eqref{eq:estimand} to be computable, the model must factor into
independently swappable pieces:
\begin{equation}
\widehat{Y} \;=\; g\big(\, \henv(E),\; \tau(p),\; \ell \,\big),
\label{eq:factorization}
\end{equation}
with \henv{} the environment representation (Phase A), $\tau(p)$ the player's
talent channel (Phase C), and $\ell$ the deployment levers. Phase B is $g$.
This factorization is not an aesthetic; it is the handle the intervention pulls.

\section{The central design decision: identity-freeness}
\label{sec:identity}
The most important sentence in this paper: \textbf{the tower never sees the
player it is describing the ice for} --- no ID, no statistics, no priors, no
deployment history. Three designs were considered.

\paragraph{Rejected: the monolith.} One network eating player + environment +
usage. It would predict well and answer nothing: with all factors entangled,
``swap the team'' has no handle --- the internal representation of the player is
partly a representation of his linemates and his team's system, and the
environment effect is confounded by every player who selected into that
environment.

\paragraph{Rejected: the firewalled two-stream (our own prior design).}
The legacy Phase~A (still on disk as \texttt{encoder.py}; deprecated July 2026)
placed a focal-identity stream and a context stream in one module, the context
side reading a gradient-detached identity summary through a one-way attention
``firewall.'' The audit verdict: such firewalls are \emph{promises, not proofs}.
Gradient paths can be blocked; information paths through shared batch
statistics and co-adapted training dynamics cannot be certified, and every leak
is invisible until it surfaces as a confidently wrong answer on exactly the rows
we sell --- movers. The cheapest firewall is absence.

\paragraph{Chosen: absence, plus a separate frozen talent channel.}
The tower's inputs are surroundings only; the player enters once, in Phase B,
through the pre-computed channel $\tau(p)$ into which no gradient flows.
``Swap the environment'' becomes a literal code path: recompute \henv{} with the
destination's people and context; $\tau(p)$ does not move.

\begin{keybox}
\textbf{The residual threat: roster fingerprinting.} Five teammate IDs nearly
identify the team, the line, and often the focal player (who else centers
Draisaitl and Hyman?). A tower that learns ``this WITH-set $\Rightarrow$ elite
production'' has partially memorized the focal player without seeing his ID ---
and at $\dodo{p \text{ leaves}}$ the old ice keeps his credit, mispricing both
sides of every star trade. Early designs \emph{mitigated} this (dropout, probes,
K-1). Section~\ref{sec:oxf} eliminates it structurally.
\end{keybox}

\subsection{Structural elimination: the OXF stack (v2.3)}
\label{sec:oxf}
A four-designer, fourteen-attack adversarial panel (July 2026; ADR-001)
established two facts. \emph{Routing alone fails:} excluding $p$'s focal rows
from the tower that scores him still permits a \emph{player-generic} completion
circuit --- ``retrieve the habitual completer of this WITH-set and add his
quality'' --- learned from other players' rows and executed for $p$ at scoring.
\emph{Reward-removal alone fails:} any provided quality scalar under-explains
identity somewhere (EB shrinkage, form drift, pair chemistry), and the residual
is identity-shaped, re-funding the circuit. Elimination is a \textbf{conjunction}:

\begin{enumerate}[leftmargin=1.5em,itemsep=2pt]
\item \textbf{Orthogonalized labels (no reward).} Every tower trains on
$\tilde{Y}(w) = Y(w) - \hat{\tau}(\mathrm{focal}, w)$ with $\hat{\tau}$
\emph{unshrunk}, \emph{split-sample} (fit on the focal's windows disjoint from
$w$), out-of-fold, identity-blind. The focal component of the label is mean-zero
given the inputs, so inferring the missing man pays zero loss reward in every
fold. Unshrunk and split-sample are load-bearing: a shrunk $\hat\tau$ leaves an
identity-correlated residual that quietly re-funds completion.
\item \textbf{Player-fold cross-fitting, shared nothing (no data).} $K{=}5$
folds of players; tower $T_k$ never trains on a row whose focal is in fold $k$;
player $p$ is always scored by $T_{k(p)}$ --- \emph{the tower that scores you
never studied you}, mirroring the existing OOF talent discipline. Per-fold
embedding tables, normalization and early-stopping state; a fold contract
asserted in the data loader.
\item \textbf{Fold discipline through the trunk.} The trunk holds
$\tau(p)\oplus\mathrm{bio}$ --- a quasi-ID --- beside $Y$; routing must not stop
at the tower. $K$ trunks train on cached out-of-fold \henv{}; serving routes the
tower by the window's focal-of-record and the trunk by the projected player.
\item \textbf{Synthetic dropout deleted (no manufactured holes).} Masking a real
contributor while $Y$ keeps his contribution is a forced-misattribution factory
(three independent attacks converged here). UNK robustness comes from
talent-gated substitution: only shell-sufficient (near-zero-talent) members may
be masked.
\item \textbf{Member talent scalars in the shell,} computed exact pairwise
leave-focal-out: member quality gains a legal absorber; ID vectors are freed for
style. The P3 probe's baseline stays \emph{unconditioned} on them.
\item \textbf{Leave-focal-out team priors} close the prior-echo channel (a
team's xG prior currently contains the focal's own past production).
\item \textbf{Probes as falsification, never tuning.} Per-fold out-of-sample
P3-incremental (gate $R^2_{\mathrm{incr}} < 0.01$), completion probe, sibling
parity; a red probe files a bug, never a re-roll. All confidence intervals
cluster-bootstrap by game (sibling rows share outcomes).
\item \textbf{The honest floor.} Glued duos ($\ge$85\% co-occurrence) are
unidentifiable by \emph{any} estimator --- the RAPM identifiability floor, not
leakage. A duo census routes their counterfactuals to
\texttt{extrapolated:true} or \texttt{REFUSED\_OOS}. Refusal is the feature.
\end{enumerate}

\noindent\textbf{Scoped claim.} The per-player fingerprint pathway is
structurally eliminated: no reward anywhere (1), no data in any scoring path
(2--3), no shared state (2), no manufactured hidden-member rows (4). Remaining
residuals: $\hat\tau$ estimation error (mean-zero $\Rightarrow$ variance, not
bias) and the identifiability floor (flagged, refused). Cost: $5\times$ tower
runs $+\,5\times$ cheap trunk runs --- one GPU weekend.

\noindent\textbf{Why this is the market edge, not hygiene.} The betting market
prices movers on trailing statistics --- co-occurrence credit. A fingerprinting
tower inherits a cousin of the \emph{same} bias, shrinking model-vs-market
disagreement exactly where we bet. OXF removes co-occurrence-fingerprint credit
from the environment and prices the player only through his own orthogonalized
channel, so disagreements concentrate on star-adjacent movers and
stayers-after-departure --- the two seams the market systematically misprices.

\section{Inputs: every seat earned, every ban evidenced}
Governing law, enforced at import by \texttt{contracts/tower\_schema.py}: every
input is \textsc{synth} (exactly constructible for a hypothetical destination
from pre-$t_0$ data), \textsc{marg} (servable as a distribution via the slot
bootstrap), or \textsc{banned}. The test is serving-time honesty: could we
produce this number on trade day, for a trade that has not happened?

\subsection{The people (the intervention itself)}
\begin{itemize}[leftmargin=1.2em,itemsep=2pt]
\item \textbf{Member identities} (\texttt{with\_ids}, \texttt{vs\_ids},
$\le\!5$ per side): learned 96-d vectors from a deliberately starved shared
table ($\sim$1{,}700 players). Who is beside and against him is the largest
environmental fact and the one the v0 baseline cannot see.
\item \textbf{Exposure} (\texttt{with\_seconds}, \texttt{vs\_seconds}): how much
of each human; drives the pooling bias (\S\ref{sec:pool}).
\item \textbf{Dynamic shells} (per member, as of game date): age, position,
handedness, \emph{season-lagged} recent form, and the member's own
games-since-team-change. The shell distinguishes 2019-Kane from 2025-Kane under
one ID vector. Form is season-lagged by construction (the F-1 echo rule): form
earned \emph{next to} the focal player reflects the focal player back into
\henv{} --- identity by reflection. Measured: naive-current form correlates
$0.310$ with focal talent; lagged form $0.267$; the survivor is genuine
assortative line-building the tower \emph{should} see.
\end{itemize}

\subsection{The situation, the bench, the schedule}
Score bucket, period and time bucket; zone start, faceoff location, start
regime, entry mode, stoppage class, after-icing (with OZ/DZ splits; on-the-fly
entries measured $\sim$12\% better than DZ faceoffs; zone information decays
with $\sim$20\,s half-life --- probed, \S\ref{sec:probes}); home/away, rink id,
bench rights, long change, skater differential. Team priors (pace, xG rates,
EB-shrunk goalie tier, both teams; all strictly pre-game and lag-audited);
coach id + tenure (82 coaches, shrinkage; a new coach is UNK with tenure 0,
itself a signal); rest days and back-to-backs (audited: 13.6\% b2b rate);
focal \texttt{games\_since\_team\_change} as an \emph{explicit} input (F-2), so
the settling curve is modeled rather than smeared; entry-side timing features
(decisions made before the exposure).

\subsection{Banned, with evidence}
\begin{center}
\begin{tabular}{@{}p{0.34\textwidth}p{0.58\textwidth}@{}}
\toprule
\textbf{Banned} & \textbf{Reason (measured where applicable)} \\
\midrule
the focal player, in any form & \S\ref{sec:identity}; the core discipline \\
\texttt{duration} as input & windows end at whistles; whistles correlate with
events; stop-bias $+51\%$. Survives only as a loss weight \\
exit-side timing & players leave \emph{because} of what happened;
outcome-caused $\Rightarrow$ label peeking. Entry-side twin stays legal ---
the asymmetry is the point \\
in-window event counts & outcomes wearing feature costumes \\
season / era ids & undefined at serving; era enters honestly via drifting team
priors \\
matchup-quality \%, standings prior & traced to leaky legacy computations
(realized full-game overlap weights; unverifiable as-of branch) \\
focal deployment priors & they describe the \emph{old} coach's choices; the
destination role template is a lever, not an environment fact \\
\bottomrule
\end{tabular}
\end{center}

\section{Architecture}
\subsection{Member representation: static core $\oplus$ dynamic shell}
\begin{equation}
m_j = \mathrm{MLP}\big(\, e_{\mathrm{id}(j)} \oplus s_j \,\big), \qquad
s_j = [\,\text{age},\ \text{pos},\ \text{hand},\ \text{lagged form},\
\text{member gsc}\,].
\end{equation}
Identity vectors carry what is stable; shells carry what changes. The split is
also the \textbf{UNK mode}: an unseen player (an AHL call-up today; an entire
AHL roster in the future recruiting product) receives the UNK vector plus a
real shell --- graceful degradation from ``I know this man'' to ``I know his
type.''

\subsection{Pooling: seconds-biased attention}
\label{sec:pool}
\begin{equation}
a_j \propto \exp\big( q^\top m_j + \log \mathrm{sec}_j \big), \qquad
h_{\mathrm{with}} = \textstyle\sum_j a_j\, m_j .
\end{equation}
Not a mean (a 3-second cameo would equal a full shift), not a max (one member
dominates), not plain attention (over-focus; resurrects fingerprinting). The
$\log$-seconds bias makes exposure the prior that attention adjusts around.
Padding (id 0, seconds 0) is masked exactly; audited at 100\% consistency over
200k sampled windows.

\subsection{Context, fusion, and size}
\begin{equation}
\henv = \mathrm{Fusion}\big([\, h_{\mathrm{with}},\, h_{\mathrm{vs}},\,
h_{\mathrm{ctx}} \,] + \mathrm{CLS}\big) \in \mathbb{R}^{256},
\end{equation}
with two pre-norm attention blocks: context must \emph{modulate} how the people
matter (the same five opponents mean different things protecting a lead versus
chasing). Total $\sim$2M parameters, and small is a feature: 6.5M windows
sounds large, but each identity vector learns only from that player's
appearances. A large tower memorizes windows; a starved one is forced to learn
hockey. The GBDT twin (\S\ref{sec:phaseb}) referees exactly this.

\section{Training, and every trap we know about}
\subsection{No loss of its own}
The tower trains end-to-end with the Phase B trunk against window outcomes:
``environment quality'' is \emph{defined} as whatever representation makes the
trunk right across two million windows. The price is that Phase B pathologies
can reach the tower through the gradient --- hence the plumbing below.

\subsection{The weighting stack (who gets a vote)}
\begin{center}
\begin{tabular}{@{}p{0.40\textwidth}p{0.52\textwidth}@{}}
\toprule
\textbf{Mechanism} & \textbf{Prevents} \\
\midrule
loss $\times$ seconds (exposure weight) & low-minute windows dominating: a
6-second rate observation gets $\sim$1/100 the vote of a 10-minute stretch \\
heteroscedastic heads (predict $\mu,\sigma$) & noisy windows steering: Gaussian
NLL divides error by $\sigma^2$, auto-muting short exposures \\
switch-weighting $\times 3$ post-move & the regime we sell drowning in the
settled majority; safe because gsc is an explicit input \\
\texttt{is\_multistint} downweight & blended-row noise \\
EB shrinkage on $\tau(p)$ (Phase C) & a 40-career-minute player carrying an
extreme talent value anywhere \\
\bottomrule
\end{tabular}
\end{center}

\subsection{The probe scorecard (every epoch; red rejects the checkpoint)}
\label{sec:probes}
\begin{center}
\begin{tabular}{@{}p{0.22\textwidth}p{0.40\textwidth}p{0.30\textwidth}@{}}
\toprule
\textbf{Probe} & \textbf{Question} & \textbf{Red means} \\
\midrule
P3-incremental & does \henv{} predict focal talent beyond raw teammate-quality
features? & roster fingerprint; widen dropout, starve IDs \\
zone-decay & does the zone-start effect decay at the measured $\sim$20\,s
half-life? & start effects smeared over windows \\
era & can \henv{} identify the season beyond team priors? & time travel at
serving \\
coach & does the coach embedding explain variance beyond roster? &
(want \emph{some}) scheme vs.\ roster proxy \\
UNK-degradation & replace members with UNK+shell: graceful drop? & tower
depends on memorized identity; AHL mode dead \\
\bottomrule
\end{tabular}
\end{center}
Era-split checkpoints ($\le$2021/22/23/24); all ablations era-fixed. The
2018--19 season currently trains shell-only for member form (no prior season on
the surface until the 2017--18 build lands); if that build stalls, the season is
excluded rather than trained on a hole.

\section{The joint with Phase B}
\label{sec:phaseb}
\begin{equation}
x = [\, \henv \oplus \tau(p) \oplus \mathrm{bio} \,] \;\rightarrow\;
4\times768\ \text{SwiGLU residual trunk, FiLM}(\ell_{1:17})
\;\rightarrow\; 10\ \text{heads}.
\end{equation}
\textbf{Three pipes, physically separate.} $\tau(p)$ is frozen (no gradient);
the 17 deployment levers enter via FiLM modulation --- they \emph{reshape} the
computation rather than add to it, which is what later answers ``what if we
used him differently?'' without retraining. \textbf{Heads:} MoneyPuck xG
for/against as primary (heteroscedastic Gaussian) with rush/rebound/chaos
splits; in-house xG as auxiliary witness; counts as Poisson with exposure
offsets; Kendall--Gal weighting across heads. \textbf{The legitimate firewall:}
micro-stat heads (hits/giveaways/takeaways) are gradient-detached from the
tower --- arena scorers disagree by up to $2.25\times$ on giveaways (T19), and
that noise may not sculpt \henv{}. Unlike \S\ref{sec:identity}'s rejected
firewall, a gradient detach is a one-line mechanical guarantee against a
non-adversarial threat: different threat class, different confidence.
\textbf{Two gates, two questions:} the tower must beat the slot-average
environment in era-fixed ablation (do specific humans help?); the trunk must
beat a GBDT twin on the same tabular inputs (is the neural machinery earning
its keep?).

\section{The joint with Phase C}
\label{sec:k1}
\subsection{Talent as a residual}
\begin{equation}
\tau(p) = \mathrm{EBshrink}\!\left( \sum_{w \in \mathcal{W}_p}
\lambda^{\Delta t_w}\big[\, y_w - \mu_{\mathrm{base}}(E_w) \,\big] \right),
\end{equation}
decay-weighted, league-demeaned, out-of-fold (the baseline never saw the
windows it judges), shrunk toward zero with fitted $K$ in effective minutes.
This channel is the engine of the already-proven 7.6\% harness win.

\subsection{The double-counting obligation (K-1)}
If the baseline $\mu_{\mathrm{base}}$ is identity-blind, then $\tau(p)$
contains credit that belongs to $p$'s linemates. Upgrading the environment
model to one that \emph{does} credit linemates (the tower) while keeping the
old residuals counts the same value twice:
\begin{equation}
\underbrace{\henv \ \text{claims Draisaitl}}_{\text{new}} \;+\;
\underbrace{\tau(\text{McDavid-adjacent}) \ \text{still contains Draisaitl}}_{\text{old}}
\;\Rightarrow\; \text{systematic overprediction for stars-adjacent movers.}
\end{equation}
In v0 the two errors partially cancel; the tower breaks the cancellation ---
and the failure lands on exactly the GM question (``is he real without 97?'').
Hence hard ship-gate K-1: before v1 ships, talent is re-derived as the residual
against the \emph{tower's} environment (one EM round), and the top/bottom-15
sniff must re-rank sensibly. Non-negotiable.

\subsection{The v2 frontier (not in the MVP)}
A style vector (rush sniper / net-front / point bomber; 13{,}708 pre-computed
shot-personality cards) interacted with the tower's people-vectors becomes the
chemistry engine --- gated behind an identifiability census, because chemistry
claims without co-occurrence support are astrology.

\section{Serving: from hypothetical to number}
Query: player $\to$ destination $\to$ role. The scenario builder bootstraps
$\times 2000$ over the destination slot's \emph{real} pre-$t_0$ windows,
weighted by the joint future schedule (opponent, venue, rest --- never
independent marginals; no Frankenstein windows), integrates games 1..40 of the
settling curve via gsc, and emits projected on-ice xGF\% with a conformal band
whose coverage was \emph{measured} at 80.0\% against an 80\% claim on 860
historical moves --- binned by evidence volume $\times$ intended role delta
(K-2: a third-liner queried as a first-liner draws his band from the
wide-change error pool). Outside joint support: \texttt{extrapolated: true};
far outside: \texttt{REFUSED\_OOS}. Refusal is a feature; it is what makes the
other answers credible.

\section{MVP alignment --- and honest disalignment}
\textbf{The MVP bar (July 2026):} proof sufficient for an NHL team partnership
or seed funding: the engine (v0 beats the industry baseline by 7.6\%, CI clear),
sealed September predictions, the public scoreboard, and the market-calls log
(gated by its own backtest). One target, one event, one raise.

\subsection*{Where the tower serves the goal}
(i) The upgrade path with a floor: v1 ships only if it beats v0 on the same
860-move harness, CI-clear, all seven gates; October cannot be hurt by the
attempt. (ii) The demo moment: v0 cannot answer ``and with Kane instead?'' ---
the tower can; interactivity is what makes the demo an engine rather than a
spreadsheet. (iii) The differentiation claim ``first causal simulation engine
in sports'' requires \dodo{\cdot}-capable machinery; \eqref{eq:factorization}
is that machinery, defensible in diligence. (iv) UNK/shell mode is the AHL
recruiting product's front door --- the expansion pitch shares the tower.

\subsection*{Where it does not serve the goal (read this too)}
(i) October does not require it; if GPU access slips past mid-August, the
correct call is to seal v0 and keep training. (ii) The market-calls leg
deliberately does not use it (shot cards + role minutes + v0 environment;
fewer moving parts under deadline). (iii) It charges the K-1 tax --- real
re-validation days v0 never costs. (iv) Its risk is real: the honest prior is
a modest first-try harness gain over v0, because the talent channel --- which
both share --- carries most of the signal. The gates exist because
``neural $=$ better'' is a hypothesis, not an entitlement.

\section{Questions the reader should ask (the grill list)}
\begin{enumerate}[leftmargin=1.4em,itemsep=2pt]
\item \emph{If the tower never sees the player, how is the projection about
him?} --- Phase B injects him via $\tau(p)$; the tower prices the ice for a
generic player, talent shifts it to him. Chemistry is v2; ask what deferring
it costs.
\item \emph{Five teammate IDs nearly name him --- why isn't that fatal?} ---
dropout + P3-incremental + K-1; demand the probe numbers on the first real
checkpoint.
\item \emph{Why allow teammate form at all?} --- season-lagged only; the
surviving correlation is measured assortativity; exact pairwise leave-focal-out
is v1.1.
\item \emph{What if the tower fails?} --- v0 ships; the company never depends
on the net.
\item \emph{Why believe the bands?} --- measured 80.0\% on 860 real moves,
per-cell after K-2; extrapolations flagged, not disguised.
\item \emph{Weakest input?} --- serving-time opponent lineups (team known,
five sampled); a standing sensitivity ablation owns it.
\item \emph{Does any of this delay October?} --- no; GPU is the only gating
resource, and v0 is the floor.
\end{enumerate}

\section*{Status ledger (July 22, 2026)}
Training surface: \textsc{built} --- 6.49M windows, 7 seasons, member shells
aligned; lag-audit \textsc{flagged 0}; deep audit 15 checks \textsc{all clear}
$\times$3 seasons. Feature legality: enforced in code. Tower+trunk v2.2:
specified here; \texttt{scripts/19} implements next (the on-disk
\texttt{encoder.py} is the deprecated two-stream --- do not train it). GPU:
\textbf{the only blocker}. Ship gates: seven, in
\texttt{ARCHITECTURE\_PLAN.md} \S5.

\vspace{6pt}
\noindent\rule{\textwidth}{0.4pt}\\
\small\emph{Internal references: \texttt{ARCHITECTURE\_PLAN.md} v2.2 \textperiodcentered{}
\texttt{PHASE\_A\_FEATURES.md} \textperiodcentered{} \texttt{AUDITOR\_GUIDE.html}
\textperiodcentered{} scripts 21--25. Every number in this paper regenerates from the
repository.}
\end{document}
