\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}

\title{\textbf{OptBot: Toward the Most Accurate Sports Simulation Ever Built}\\
\large What Is Proven, What Is Built, and What Remains}
\author{OptBot Research \\ \small Status Report v1.0 --- July 2026 --- Confidential}
\date{}

\begin{document}
\maketitle

\begin{abstract}
\noindent OptBot projects what an NHL player becomes in an environment he has never
played in --- before a single shift is observed there. This report separates, without
spin, what is \emph{proven}, what is \emph{built}, and what is \emph{still to come}.
The headline: on 860 real player--team transitions spanning July 2019 through the 2025
off-season --- scored against independently licensed MoneyPuck expected-goals actuals,
with every input frozen at each move date --- the \emph{minimal} version of the system
already beats the industry-standard projection by 7.6\% (RMSE 5.74 vs.\ 6.21; bootstrap
95\% CI on the difference $[-0.61, -0.33]$, excluding zero), and its 80\% uncertainty
intervals achieve \textbf{80.0\%, 80.0\%, and 79.8\%} measured coverage across player-%
experience bins. No neural network has yet been trained: these results come from
audited statistics alone, and they define the floor --- not the ceiling --- of the
system. The neural phases (A: environment tower; B: causal trunk; C: style vectors)
are designed, coded, and gated, awaiting their first GPU hour.
\end{abstract}

\section{What Is Proven}

\subsection{The headline results}

\begin{center}
\begin{tabular}{@{}lcccc@{}}
\toprule
Projector & RMSE (xGF\%, first 40 GP) & vs.\ Marcel & 95\% CI & $n$ \\
\midrule
Last-season carryover & 7.71 & $+24\%$ worse & --- & 860 \\
Marcel (industry standard) & 6.21 & --- & --- & 860 \\
\textbf{OptBot v0} & \textbf{5.74} & $\mathbf{-7.6\%}$ & $[-0.61,\,-0.33]$ & 860 \\
\midrule
\multicolumn{5}{@{}l@{}}{\small Companion result, in-house xG actuals, 2021--2025 ledger:
v0 5.44 vs.\ Marcel 6.02 ($-9.7\%$, CI $[-0.77,-0.40]$, $n=546$).}\\
\bottomrule
\end{tabular}
\end{center}

\noindent Three properties make these numbers unusually hard to attack:
\begin{enumerate}[nosep]
\item \textbf{Frozen-clock discipline.} Every projection uses only information strictly
before its move date; an executable audit re-runs sampled moves with all post-date data
physically deleted and asserts bit-identical output.
\item \textbf{Independent actuals.} The extended backtest is scored on MoneyPuck's
expected-goals model (used with permission), not our own --- the referee is not on our
payroll. The two rulers agree at $r = 0.925$ per window.
\item \textbf{Era transport.} The margin survives seven distinct eras, including thin-%
history 2019--20, COVID seasons, and 64 summer-2025 signings scored against the
just-completed 2025-26 season. Edges that are artifacts collapse out-of-era; this one
traveled.
\end{enumerate}

\subsection{Calibration: the result behind the result}

Every projection ships with an 80\% interval fit by split-conformal inference on
historical moves. Measured coverage: \textbf{0.800 / 0.800 / 0.798} across rookie,
mid-career, and veteran bins. To our knowledge no commercial sports-projection vendor
publishes measured calibration at all; the predecessor system this project replaced
achieved 12\% at the same nominal level. Accuracy wins arguments; \emph{measured honesty}
wins contracts.

\subsection{Distance to the theoretical ceiling}

Forty games of on-ice xGF\% carries an irreducible sampling noise floor of roughly 4
RMSE points --- no model, however perfect, can beat it. Against the \emph{closable} gap
(Marcel at 6.21 down to the $\sim$4.0 floor), v0 alone --- one scalar per player plus a
destination-environment average --- has already captured $\approx 21\%$. The remaining
$\sim$1.7 points are the neural phases' hunting ground, and the reason ``most accurate
sports simulation ever built'' is a trajectory with a measured starting point rather
than a slogan.

\subsection{The data substrate (what ``certified'' means)}

The training surface (6.5M+ player-windows, ten seasons collected) passed five
independent certifications: (i) machine-checked internal contracts; (ii) external
reconciliation vs.\ MoneyPuck (95.9\% exact 5v5 goal agreement over 8,265 games);
(iii) NHL-API spot audit (94--98\% presence/event/bounds agreement); (iv) the original
builder's own zero-issue full-season token audits, rediscovered and adopted as
regression gates; (v) a full-season event microscope against official shift charts:
99.7\% of 986{,}920 player-window second-counts exact to $\le$1s, \textbf{100.00\%} of
754{,}104 personal-event attributions correct, and \textbf{zero} goals mis-credited
across 59{,}807 on-off-on substitution cases. Separately, all 617 lagged prior columns
passed an empirical prediction-symmetry test (worst leak-gap 0.005 vs.\ 0.902 for a
deliberate-leak control): the priors are \emph{provably} lagged, not assumed lagged.
Twenty-two named causal threats are tracked in a public register; each is closed,
measured, priced into the intervals, or refused at the API. Fourteen silent data
corruptions --- including an outcomes column that was identically zero across 761{,}823
rows --- were found and repaired along the way; several fixes \emph{improved} the
headline (cleaning the test set raised the measured edge from $-8.6\%$ to $-9.7\%$).

\section{What Is Built But Not Yet Trained}

v0 is deliberately minimal: destination-environment expectation plus a deconfounded,
empirical-Bayes-shrunk talent scalar. It cannot see linemates, lever settings, or
playing style. The machinery that can --- the actual Causal Intervention Network ---
is coded, unit-tested, and gated, but has consumed \textbf{zero GPU-hours}:

\begin{center}
\begin{tabular}{@{}llll@{}}
\toprule
Phase & Role & Status & Ship gate \\
\midrule
A --- Environment tower & encode \emph{who is on the ice} & coded, untrained &
5-probe leakage scorecard \\
B --- CIN trunk & levers, talent channel, outcomes & coded, untrained &
beat v0 in the 860-move harness \\
C --- Style vectors & fit \& chemistry (13,708 shot- & priors built, &
probe-gated; v2 \\
 & personality cards precomputed) & vectors unstarted & \\
\bottomrule
\end{tabular}
\end{center}

\noindent Supporting assets already banked for these phases: a per-shot attachment of
MoneyPuck's full shot model to our windows (99.86\% match; boundary-second assignment
ruled by event order --- a 7\% -of-shots bug class caught before it shipped); rush /
rebound / chaos / pressure target decompositions; entry-mode context (on-the-fly
entrants measured at $+12\%$ xGF/60 --- a selection effect the tower conditions on);
and a feature-legality schema whose banned list cites the code trace that convicted
each leaky column.

\section{What Remains}

\begin{enumerate}[nosep]
\item \textbf{First GPU run} (Phase A tower + Phase B trunk, era-split): the per-phase
feature ablations happen here, empirically, judged by the harness and the probes ---
legality was decided by trace; utility is decided by experiment.
\item \textbf{The shootout:} v1 must beat v0's 5.74 with a CI clear of zero, beat its
own gradient-boosted twin, and pass all probes --- or v0 ships. The company does not
depend on the neural result; it is upside with a floor.
\item \textbf{Phase C v2:} style vectors and pairwise fit, unlocked only after A+B ---
the chemistry claims will be gated by an identifiability census, not enthusiasm.
\item \textbf{September:} projections for every 2026-27 mover, hash-sealed before puck
drop. \textbf{October:} the sport watches them score in public. That --- accuracy,
performed live, with measured error bars --- is the world-shocking act; the numbers
above are what make it safe to attempt.
\end{enumerate}

\section*{One-Sentence Summary}

Before training a single neural network, OptBot already beats the sport's standard
projection method by 7.6\% on 860 frozen-clock trades scored by an independent referee,
with uncertainty intervals accurate to two-tenths of a percent --- and every component
that could make it dramatically better is built, audited, and waiting for its first
GPU hour.

\end{document}
